I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-22 Paper/proofs.tex
fix typos

\begin{definition}[Sign of Node]\label{sign_of_nodes}
	We define the partial sign function $S$ on neurons $n$: 	
	\begin{enumerate}
		\item $S(n)=0$ if all path from $n$ to $z$ have 0 weight; 
		\item $S(n)=1$ if all path from $n$ to $z$ hafe non-negative weight, and at least one path has a positive weight; 
		\item $S(n)=-1$ if all path from $n$ to $z$ have non-positive weight, and at least one path has a negative weight. 
	\end{enumerate}
\end{definition}

@@

			Now, we show Theorem \ref{thm:2} can prove Theorem \ref{th2}. Suppose $a$ is a node in a weak compensating path $P$, and $P,P'$ is a compensating pair.

>>>>

\begin{definition}[Sign of Node]\label{sign_of_nodes}
	We define the partial sign function $S$ on neurons $n$: 	
	\begin{enumerate}
		\item $S(n)=0$ if all path from $n$ to $z$ have 0 weight; 
		\item $S(n)=1$ if all path from $n$ to $z$ have non-negative weight, and at least one path has a positive weight; 
		\item $S(n)=-1$ if all path from $n$ to $z$ have non-positive weight, and at least one path has a negative weight. 
	\end{enumerate}
\end{definition}

@@

			Now, we show that Theorem \ref{thm:2} can prove Theorem \ref{th2}. Suppose $a$ is a node in a weak compensating path $P$, and $P,P'$ is a compensating pair.
